Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators \thanks{ An abridged version of this manuscript was presented at the ABCM International Congress of Mechanical Engineering (COBEM \colorbox{yellow}{Completar... cidade etc}). }

### 2019-11-05 PaperMagneticProfiles_JBSMSE.tex
Rename figures sequentially.

\begin{figure}[!ht]
  \centering
  \includegraphics[width=8cm]{reg3d}
  \caption{AMR model geometry}
  \label{fig:amrmodel}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=8cm]{mprofile}
  \caption{Instantaneous fluid flow profile. Adapated from \cite{bib:fortkamp20-desig}.}
  \label{fig:mprofile}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=8cm]{profiles_it_and_rc}
  \caption{Instantaneous ("IT") and rectified cosine ("RC") magnetic profiles}
  \label{fig:itrc}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=7cm]{profile_rm}
  \caption{\textcolor{black}{Magnetic ramp}  profile}
  \label{fig:ramp}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
\includegraphics[width=8cm]{profiles_it_and_rc_same_minimum}
  \caption{Configuration of average and extreme values of the instantaneous and rectified cosine profiles }
  \label{fig:comparison-methods-profiles}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=7cm]{profiles_rc_and_flow_instantaneous}
  \caption{Rectified cosine magnetic profile and the instantaneous flow profile with blow fraction of \SI{60}{\percent}}
  \label{fig:cos-inst-60}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
\includegraphics[width=8cm]{Qc_B_comp_f_1_same_minimum}
  \caption{Cooling capacity as a function of the  average high magnetic field, for different utilizations. \textcolor{black}{``IT''}: instantaneous (blow fraction of \SI{100}{\percent}); ``RC'': rectified cosine  (blow fraction of \SI{60}{\percent}).}
 \label{fig:cos_ins}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
\includegraphics[width=7cm]{COP_B_comp_f_1_same_minimum}
  \caption{Coefficient of performance as a function of the  average high magnetic field, for different values of utilization. ``IT'': instantaneous (blow fraction of \SI{100}{\percent}); ``RC'': rectified cosine  (blow fraction of \SI{60}{\percent}).}
 \label{fig:cos_ins_cop}
\end{figure}

\begin{figure}[!ht]
  \centering
  \includegraphics[width=10cm]{W_B_comp_f_1_Phi_60_same_minimum}
  \caption{Power contributions as functions of the average high magnetic field, for a utilization of 0.6. ``IT'': instantaneous (blow fraction of \SI{100}{\percent}); ``RC'': rectified cosine  (blow fraction of \SI{60}{\percent}).}
  \label{fig:cos_ins_w}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
\subfloat[$f = \SI{1}{\hertz}$]{\includegraphics[width=8cm]{Qc_Phi_inst_f_1_Hmin_005_FB_100}\label{fig:Qc_phi_inst_1}}
\,
  \subfloat[$f = \SI{2}{\hertz}$]{\includegraphics[width=8cm]{Qc_Phi_inst_f_2_Hmin_005_FB_100}\label{fig:Qc_phi_inst_2}}
  \caption{Cooling capacity as a function of utilization, for various values of the high magnetic field  for the instantaneous profile}
  \label{fig:qc_phi_inst}
\end{figure}

\begin{figure}[!ht]
  \centering
  \subfloat[Cooling capacity]{\includegraphics[width=9cm]{Qc_H_inst_f_1_Phi_40}\label{fig:Qc_H_inst_f_1_Phi_40}}
\quad
  \subfloat[Coefficient of performance]{\includegraphics[width=9cm]{COP_H_inst_f_1_Phi_40}\label{fig:COP_H_inst_f_1_Phi_40}}
  \caption{Performance metrics as a function of the regenerator height (all other parameters were set as in Table~\ref{tab:params-cobem}, for utilization factor of 0.4) for various values of the high magnetic field of the instantaneous profile}
\label{fig:Qc_H_inst}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=7cm]{amr-casing}
  \caption{Model for the casing losses in regenerators}
  \label{fig:amr-casing}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=7cm]{profiles_rm_and_flow_instantaneous}
  \caption{Comparison between the magnetic \textcolor{black}{ramp} profile (solid line) and the instantaneous fluid flow profile (dashed line)}
  \label{fig:ramp-inst}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \subfloat[Cooling capacity]{\includegraphics[width=5cm]{Qc_FM_ramp_f_1_Phi_40_35K_1300mT}\label{fig:Qc_FM_ramp_f_1_Phi_40_35K_1.3T}}
\quad
 \subfloat[Coefficient of performance]{\includegraphics[width=5cm]{COP_FM_ramp_f_1_Phi_40_35K_1300mT}\label{fig:COP_FM_ramp_f_1_Phi_40_35K_1.3T}}
  \caption{Performance of the AMR system for various blow and magnetization fractions, utilization of 0.4 and and high magnetic field of \SI{1.3}{\tesla}}
  \label{fig:Qc_COP_curves_phi40}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \subfloat[$\Phi = \num{0.2}$]{\includegraphics[width=5cm]{Qc_FM_ramp_f_1_Phi_20_35K_1300mT}\label{fig:Qc_FM_ramp_f_1_Phi_20_35K_1.3T}}
\quad
 \subfloat[$\Phi = \num{
0.5}$]{\includegraphics[width=5cm]{Qc_FM_ramp_f_1_Phi_50_35K_1300mT}\label{fig:COP_FM_ramp_f_1_Phi_50_35K_1.3T}}
  \caption{Influence of utilization on the cooling capacity of the AMR system for  various blow and magnetization fractions, with high magnetic field of \SI{1.3}{\tesla}}
  \label{fig:Qc_curves_ramp_phi}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \subfloat[$\Phi = 0.2, F\ped{B} = \SI{60}{\percent}$]{\includegraphics[width=5cm]{COP_ramp_map_f_1_Phi_20_FB_60_35K_Valv_ASCO}\label{fig:COP_ramp_map_f_1_Phi_20_FB_70_35K_Valv_ASCO}}
\quad
 \subfloat[$\Phi= 0.2, F\ped{B} = \SI{90}{\percent}$]{\includegraphics[width=5cm]{COP_ramp_map_f_1_Phi_20_FB_90_35K_Valv_ASCO}\label{fig:COP_ramp_map_f_1_Phi_20_FB_90_35K_Valv_ASCO}} \\
  \subfloat[$\Phi = 0.4, F\ped{B} = \SI{60}{\percent}$]{\includegraphics[width=5cm]{COP_ramp_map_f_1_Phi_40_FB_60_35K_Valv_ASCO}\label{fig:COP_ramp_map_f_1_Phi_60_FB_90_35K_Valv_ASCO}}
\quad
 \subfloat[$\Phi = 0.4, F\ped{B} = \SI{90}{\percent}$]{\includegraphics[width=5cm]{COP_ramp_map_f_1_Phi_40_FB_90_35K_Valv_ASCO}\label{fig:COP_ramp_map_f_1_Phi_40_FB_90_35K_Valv_ASCO}}
  \caption{Influence of utilization and blow fraction on the coefficient of performance of the AMR system for varying high magnetic field and magnetization fraction}
  \label{fig:COP_maps_ramp_FM}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
\subfloat[Cooling capacity (solid lines) and coefficient of performance (dashed lines)]{  \includegraphics[width=5cm]{Qc_COP_combined_H_regW30}\label{fig:Qc_COP_Hreg}}
\,
\subfloat[Second-law efficiency]{\includegraphics[width=5cm]{eta_H_regW30}\label{fig:eta_Hreg}}
  \caption{Performance of the AMR with varying regenerator height and high magnetic field, with fixed $F\ped{M} = F\ped{B} = \SI{70}{\percent}$ and $\Phi = 0.4$}
  \label{fig:qc-cop-eta-amr-height}
\end{figure}

>>>>

\begin{figure}[!ht]
  \centering
  \includegraphics[width=8cm]{Fig1-reg3d}
  \caption{AMR model geometry}
  \label{fig:amrmodel}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=8cm]{Fig2-mprofile}
  \caption{Instantaneous fluid flow profile. Adapated from \cite{bib:fortkamp20-desig}.}
  \label{fig:mprofile}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=8cm]{Fig3-profiles_it_and_rc}
  \caption{Instantaneous ("IT") and rectified cosine ("RC") magnetic profiles}
  \label{fig:itrc}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=7cm]{Fig4-profile_rm}
  \caption{\textcolor{black}{Magnetic ramp}  profile}
  \label{fig:ramp}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
\includegraphics[width=8cm]{Fig5-profiles_it_and_rc_same_minimum}
  \caption{Configuration of average and extreme values of the instantaneous and rectified cosine profiles }
  \label{fig:comparison-methods-profiles}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=7cm]{Fig6-profiles_rc_and_flow_instantaneous}
  \caption{Rectified cosine magnetic profile and the instantaneous flow profile with blow fraction of \SI{60}{\percent}}
  \label{fig:cos-inst-60}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
\includegraphics[width=8cm]{Fig7-Qc_B_comp_f_1_same_minimum}
  \caption{Cooling capacity as a function of the  average high magnetic field, for different utilizations. \textcolor{black}{``IT''}: instantaneous (blow fraction of \SI{100}{\percent}); ``RC'': rectified cosine  (blow fraction of \SI{60}{\percent}).}
 \label{fig:cos_ins}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
\includegraphics[width=7cm]{Fig8-COP_B_comp_f_1_same_minimum}
  \caption{Coefficient of performance as a function of the  average high magnetic field, for different values of utilization. ``IT'': instantaneous (blow fraction of \SI{100}{\percent}); ``RC'': rectified cosine  (blow fraction of \SI{60}{\percent}).}
 \label{fig:cos_ins_cop}
\end{figure}

\begin{figure}[!ht]
  \centering
  \includegraphics[width=10cm]{Fig9-W_B_comp_f_1_Phi_60_same_minimum}
  \caption{Power contributions as functions of the average high magnetic field, for a utilization of 0.6. ``IT'': instantaneous (blow fraction of \SI{100}{\percent}); ``RC'': rectified cosine  (blow fraction of \SI{60}{\percent}).}
  \label{fig:cos_ins_w}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
\subfloat[$f = \SI{1}{\hertz}$]{\includegraphics[width=8cm]{Fig10a-Qc_Phi_inst_f_1_Hmin_005_FB_100}\label{fig:Qc_phi_inst_1}}
\,
  \subfloat[$f = \SI{2}{\hertz}$]{\includegraphics[width=8cm]{Fig10b-Qc_Phi_inst_f_2_Hmin_005_FB_100}\label{fig:Qc_phi_inst_2}}
  \caption{Cooling capacity as a function of utilization, for various values of the high magnetic field  for the instantaneous profile}
  \label{fig:qc_phi_inst}
\end{figure}

\begin{figure}[!ht]
  \centering
  \subfloat[Cooling capacity]{\includegraphics[width=9cm]{Fig11a-Qc_H_inst_f_1_Phi_40}\label{fig:Qc_H_inst_f_1_Phi_40}}
\quad
  \subfloat[Coefficient of performance]{\includegraphics[width=9cm]{Fig11b-COP_H_inst_f_1_Phi_40}\label{fig:COP_H_inst_f_1_Phi_40}}
  \caption{Performance metrics as a function of the regenerator height (all other parameters were set as in Table~\ref{tab:params-cobem}, for utilization factor of 0.4) for various values of the high magnetic field of the instantaneous profile}
\label{fig:Qc_H_inst}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=7cm]{Fig12-amr-casing}
  \caption{Model for the casing losses in regenerators}
  \label{fig:amr-casing}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=7cm]{Fig13-profiles_rm_and_flow_instantaneous}
  \caption{Comparison between the magnetic \textcolor{black}{ramp} profile (solid line) and the instantaneous fluid flow profile (dashed line)}
  \label{fig:ramp-inst}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \subfloat[Cooling capacity]{\includegraphics[width=5cm]{Fig14a-Qc_FM_ramp_f_1_Phi_40_35K_1300mT}\label{fig:Qc_FM_ramp_f_1_Phi_40_35K_1.3T}}
\quad
 \subfloat[Coefficient of performance]{\includegraphics[width=5cm]{Fig14b-COP_FM_ramp_f_1_Phi_40_35K_1300mT}\label{fig:COP_FM_ramp_f_1_Phi_40_35K_1.3T}}
  \caption{Performance of the AMR system for various blow and magnetization fractions, utilization of 0.4 and and high magnetic field of \SI{1.3}{\tesla}}
  \label{fig:Qc_COP_curves_phi40}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \subfloat[$\Phi = \num{0.2}$]{\includegraphics[width=5cm]{Fig15a-Qc_FM_ramp_f_1_Phi_20_35K_1300mT}\label{fig:Qc_FM_ramp_f_1_Phi_20_35K_1.3T}}
\quad
 \subfloat[$\Phi = \num{
0.5}$]{\includegraphics[width=5cm]{Fig15b-Qc_FM_ramp_f_1_Phi_50_35K_1300mT}\label{fig:COP_FM_ramp_f_1_Phi_50_35K_1.3T}}
  \caption{Influence of utilization on the cooling capacity of the AMR system for  various blow and magnetization fractions, with high magnetic field of \SI{1.3}{\tesla}}
  \label{fig:Qc_curves_ramp_phi}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \subfloat[$\Phi = 0.2, F\ped{B} = \SI{60}{\percent}$]{\includegraphics[width=5cm]{Fig16a-COP_ramp_map_f_1_Phi_20_FB_60_35K_Valv_ASCO}\label{fig:COP_ramp_map_f_1_Phi_20_FB_70_35K_Valv_ASCO}}
\quad
 \subfloat[$\Phi= 0.2, F\ped{B} = \SI{90}{\percent}$]{\includegraphics[width=5cm]{Fig16b-COP_ramp_map_f_1_Phi_20_FB_90_35K_Valv_ASCO}\label{fig:COP_ramp_map_f_1_Phi_20_FB_90_35K_Valv_ASCO}} \\
  \subfloat[$\Phi = 0.4, F\ped{B} = \SI{60}{\percent}$]{\includegraphics[width=5cm]{Fig16c-COP_ramp_map_f_1_Phi_40_FB_60_35K_Valv_ASCO}\label{fig:COP_ramp_map_f_1_Phi_60_FB_90_35K_Valv_ASCO}}
\quad
 \subfloat[$\Phi = 0.4, F\ped{B} = \SI{90}{\percent}$]{\includegraphics[width=5cm]{Fig16d-COP_ramp_map_f_1_Phi_40_FB_90_35K_Valv_ASCO}\label{fig:COP_ramp_map_f_1_Phi_40_FB_90_35K_Valv_ASCO}}
  \caption{Influence of utilization and blow fraction on the coefficient of performance of the AMR system for varying high magnetic field and magnetization fraction}
  \label{fig:COP_maps_ramp_FM}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
\subfloat[Cooling capacity (solid lines) and coefficient of performance (dashed lines)]{  \includegraphics[width=5cm]{Fig17a-Qc_COP_combined_H_regW30}\label{fig:Qc_COP_Hreg}}
\,
\subfloat[Second-law efficiency]{\includegraphics[width=5cm]{Fig17b-eta_H_regW30}\label{fig:eta_Hreg}}
  \caption{Performance of the AMR with varying regenerator height and high magnetic field, with fixed $F\ped{M} = F\ped{B} = \SI{70}{\percent}$ and $\Phi = 0.4$}
  \label{fig:qc-cop-eta-amr-height}
\end{figure}
